Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

\extraspacing {\bf Problem $\bm{\mathscr{B}}$.} The input involves a set $H$ of horizontal segments and a set $V$ of vertical segments, all in 2D space. The goal is to report, for each segment $h \in H$, the leftmost point $p$ on $h$ such that $p$ is on some vertical segment in $V$. If $h$ does not intersect with any segment in $V$, report nothing for $h$. Figure~\ref{fig:probs}a gives an example where $H = \set{h_1, h_2, h_3}$ and $V = \set{v_1, v_2}$; the output is $\set{(h_1, p_1), (h_2, p_2)}$. In Appendix~\ref{app:bricks}, we explain how to solve the problem in $O(n \log n)$ time where $n = |H| + |V|$.

@@

\extraspacing {\bf Problem $\bm{\mathscr{E}}$.} The input involves a set $H$ of horizontal segments and a set $R$ of rectangles, all in 2D space. The goal is to report, for each segment $h \in H$, all the rectangles $r \in R$ containing $h$. Furthermore, those rectangles need to be sorted by the x-coordinates of their right boundaries. Formally, if $r_1, r_2, ..., r_z$ (for some $z \ge 1$) are all the rectangles in $R$ containing $h$, we output $(h: r_1, r_2, ..., r_z)$, provided that $\xright(r_i) \ge \xright(r_{i-1})$ for each $i \in [2, z]$. Figure~\ref{fig:probs}c gives an example where $H = \set{h_1, h_2, h_3}$ and $R = \set{r_1, r_2, r_3}$; the output is $\set{(h_1: r_2, r_1), (h_2: r_2, r_3)}$. In Appendix~\ref{app:bricks}, we explain how to solve the problem in $O(n \log n + \out)$ time where $n = |H| + |R|$ and $\out$ is the number of pairs $(h, r) \in H \times R$ such that $r$ contains $h$.

@@

In the same fashion, we obtain the trimmed version $R_i'$ of $R_i$ for all $i \in [2, n]$, spending $O(k n \log n)$ time in total. We now solve the $(k-2)$-SJ problem on $R_1', R_2', ..., R_{k-2}'$ using the algorithm $\A$ supplied (see Lemma~\ref{lmm:hv}). This $(k-2)$-SJ clearly has an input size at most $n$, and let us represent its result as $\J(R_1', R_2, ..., R_{k-2})$. We prove in Appendix~\ref{app:hv}:

@@

We reminder the reader that $\out$ is the output size of the original H-V $k$-SJ problem. As a corollary of Lemma~\ref{lmm:hv:type1:proj}, the $(k-2)$-SJ can be settled in $F_{k-2}(n, \out)$ time.

@@

            \item Denote by $r_i$ ($i \in [k-2]$) the full rectangle of $\bm{t}[i']$. 
            For any $h \in \cross(\bm{t}, H)$ and any $v \in \cross(\bm{t}, V)$, the $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J(R_1, ..., R_{k-2}, H, V)$.

            \item If a $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J_1$, then $h \in \cross(\bm{t}, H)$ and $v \in \cross(\bm{t}, V)$.
        }

>>>>

\extraspacing {\bf Problem $\bm{\mathscr{B}}$.} The input involves a set $H$ of horizontal segments and a set $V$ of vertical segments, all in 2D space. The goal is to report, for each segment $h \in H$, the leftmost point $p$ on $h$ such that $p$ is on some vertical segment in $V$. If $h$ does not intersect with any segment in $V$, report nothing for $h$. Figure~\ref{fig:probs}b gives an example where $H = \set{h_1, h_2, h_3}$ and $V = \set{v_1, v_2}$; the output is $\set{(h_1, p_1), (h_2, p_2)}$. In Appendix~\ref{app:bricks}, we explain how to solve the problem in $O(n \log n)$ time where $n = |H| + |V|$.

@@

\extraspacing {\bf Problem $\bm{\mathscr{E}}$.} The input involves a set $H$ of horizontal segments and a set $R$ of rectangles, all in 2D space. The goal is to report, for each segment $h \in H$, all the rectangles $r \in R$ containing $h$. Furthermore, those rectangles need to be sorted by the x-coordinates of their right boundaries. Formally, if $r_1, r_2, ..., r_z$ (for some $z \ge 1$) are all the rectangles in $R$ containing $h$, we output $(h: r_1, r_2, ..., r_z)$, provided that $\xright(r_i) \ge \xright(r_{i-1})$ for each $i \in [2, z]$. Figure~\ref{fig:probs}e gives an example where $H = \set{h_1, h_2, h_3}$ and $R = \set{r_1, r_2, r_3}$; the output is $\set{(h_1: r_2, r_1), (h_2: r_2, r_3)}$. In Appendix~\ref{app:bricks}, we explain how to solve the problem in $O(n \log n + \out)$ time where $n = |H| + |R|$ and $\out$ is the number of pairs $(h, r) \in H \times R$ such that $r$ contains $h$.

@@

In the same fashion, we obtain the trimmed version $R_i'$ of $R_i$ for all $i \in [2, k]$, spending $O(k n \log n)$ time in total. We now solve the $(k-2)$-SJ problem on $R_1', R_2', ..., R_{k-2}'$ using the algorithm $\A$ supplied (see Lemma~\ref{lmm:hv}). This $(k-2)$-SJ clearly has an input size at most $n$, and let us represent its result as $\J(R_1', R_2, ..., R_{k-2})$. We prove in Appendix~\ref{app:hv}:

@@

We remind the reader that $\out$ is the output size of the original H-V $k$-SJ problem. As a corollary of Lemma~\ref{lmm:hv:type1:proj}, the $(k-2)$-SJ can be settled in $F_{k-2}(n, \out)$ time.

@@

            \item Denote by $r_i$ ($i \in [k-2]$) the full rectangle of $\bm{t}[i]$. 
            For any $h \in \cross(\bm{t}, H)$ and any $v \in \cross(\bm{t}, V)$, the $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J(R_1, ..., R_{k-2}, H, V)$.

            \item If the $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J_1$, then $h \in \cross(\bm{t}, H)$ and $v \in \cross(\bm{t}, V)$.
        }
